Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-15 PAPER.tex
Rejigger Adrians note about how loss is really a normalization issue.

{\bf In general:} Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data. However, the normalization matrix $\mathbf{M}$ is generally derived assuming that the unnormalized estimator is quadratic in the data. Thus, neglecting couplings between data and its weightings causes power spectrum estimates to be incorrectly normalized. As argued in this section, the resulting bias will tend to bias the results \emph{low}, which is simply another way of describing signal loss.

>>>>

{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.  Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data. However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data.  The power spectrum estimate will also be incorrectly normalized which manifests as signal loss. We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss, and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics
